---
title: "Modification and Prototypicality in LDP"
author: "ben morris"
date: "6/28/2019"
output: html_document
---


```{r setup}
#set up and get SQL connection
library(RMySQL)
library(SnowballC)
library(childesr)
library(tidytext)
library(tictoc)
library(ggridges)
library(tidyverse)
library(here)
library(scales)
library(tidyboot)
library(lme4)
library(feather)

source(here("read_ldp.R"))
ldp <- connect_to_ldp()
```

```{r}
list_tables <- function(connection) {
  DBI::dbListTables(connection)
}

get_table <- function(connection, name) {
  dplyr::tbl(connection, name)
}

list_tables(ldp)
get_table(ldp, "ppvt")
subs <- get_table(ldp, "subjects") %>% collect()
typ_kids <- subs %>%
  filter(lesion == "") %>% 
  filter(project == 2) %>% 
  pull(id)
```

```{r}
tic()
utts <- get_table(ldp, "utterances") %>%
  collect()
toc()
library(beep)
beep()

utts_clean <- utts %>%
  #include only typically developing participants
  filter(subject %in% typ_kids) %>%
  #grab parent utterances
  filter(!is.na(p_chat))  %>%
  #drop the many things we don't care about
  select(subject, session, p_chat, p_mor)  %>%
  #add new utt_id variable
  mutate(utt_id= row_number())

PoS <- utts_clean %>% 
  # filter(session==1) %>%
  unnest_tokens(PoS, p_mor, drop=FALSE, token = stringr::str_split, pattern = " ") %>%
  filter(PoS != "")
```


```{r}
#unnest just morph codes --> PoS
  # then split morph code into morph + word
tagged <- PoS %>%
  separate(PoS, into=c("PoS", "word"), sep="\\|") %>%
  filter(!is.na(word)) %>%
  separate(word, into=c("word", "garbage"), sep= "[^[:alnum:]]") %>%
  mutate(stem = wordStem(word)) %>%  
  select(-garbage)
```


#check noun usage consistency across ages
#correlate rank frequency across age groups for available nouns?
```{r}
ranked <- tagged %>%
  ungroup() %>%
  mutate(age_quant = ntile(tagged$session,4)) %>%
  anti_join(stop_words) %>%
  filter(stem != "") %>%
  filter(grepl("n",PoS, fixed=TRUE)) %>%
  group_by(stem, age_quant) %>%
  summarize(n=n()) %>% 
  arrange(age_quant, desc(n)) %>%
  group_by(age_quant) %>%
  mutate(rank = row_number())

ranked_wide <- ranked %>% 
  select(stem, age_quant, rank) %>% 
  spread(age_quant, rank) %>%
  rowwise() %>%
  mutate(tot_usage = sum(`1`, `2`, `3`, `4`, na.rm=TRUE)) %>%
  mutate(all_sess = if_else(is.na(`1` + `2` + `3` + `4`), F, T))

#filtered to things only in all sessions
ranked_all_sess <- ranked_wide %>% filter(all_sess==T)

cor.test(ranked_wide$`1`, ranked_wide$`2`, na.rm=TRUE)
cor.test(ranked_wide$`1`, ranked_wide$`4`, na.rm=TRUE)

```
###quick descriptives:
- 8,150 distinct nouns used across LDP (probably some more data cleaning to do...)

- seperate 12 sessions into 1 year ranges (4 bins)
- 1,829 distinct nouns, after filtering only to things in all 4 years of measurment


#grab adjectives from target nouns
```{r}
#ranked_all_sess
#only nouns used in each year starting at session 1 (i.e. sessions [1:3, 4:6, 7:9, 10:12])
target_nouns <- ranked_all_sess %>% pull(stem)


#grab target utterances with target nouns
total_utts <- tagged
target_utts <- total_utts[total_utts$stem %in% target_nouns,] %>% 
  filter(PoS== "n") %>%
  rename(noun=word,
         noun_PoS = PoS) %>% 
  select(-stem)


adj_list <- total_utts %>% 
  filter(grepl("adj", PoS)) %>%
  filter(PoS == "adj") %>%
  distinct(PoS) %>% 
  pull(PoS)

all_adjectives <- total_utts[total_utts$PoS %in% adj_list,] %>% 
  rename(adj=word,
         adj_PoS = PoS) %>% 
  select(-stem)

#all the target utts with an ajective
adj_noun_utts <- inner_join(target_utts, all_adjectives, by=c("subject", "session", "p_chat", "p_mor", "utt_id"))
 # %>% filter(adj=="")

unmod_utts <- anti_join(target_utts, adj_noun_utts, by=c("subject", "session", "p_chat", "p_mor", "utt_id")) 

#should be 0
nrow(target_utts) - nrow(adj_noun_utts) - nrow(unmod_utts)

#peek at most common pairs
adj_noun_utts %>% 
  count(adj, noun, sort=TRUE) %>%
  head(50)

#ALL pairs
adj_noun_pairs_target_full <- adj_noun_utts %>% 
  count(adj, noun, sort=TRUE) %>%
  mutate(rank = row_number()) 

#ALL pairs, split by session
adj_noun_pairs_target_session <- adj_noun_utts %>% 
  count(session, adj, noun) %>%
  arrange(session, desc(n), adj, noun)

#a ton of these pairs occur just once
adj_noun_pairs_target_full %>% filter(n==1) %>%
  group_by(adj, noun) %>% nrow
```

#Use Brysbaert threshold
```{r}
#get brysbaert concreteness
concrete_concepts <- read.csv("data/concreteness.csv") %>%
  mutate(stem= wordStem(Word)) %>%
  # filter(stem %in% target_nouns) %>%
  select(Word, stem, Conc.M, Conc.SD) %>%
  mutate(conc_rank = ntile(Conc.M,4))

#get sense of concretness range across all 40,000 items
hist(concrete_concepts$Conc.M)

most_concrete <- concrete_concepts %>%
  mutate(conc_rank = ntile(Conc.M,4)) %>%
  arrange(desc(Conc.M)) %>%
  filter(conc_rank == 4)
#using 4 bins thresholds concreteness scores of 3.89 or higher...

#filter to concrete adjective + noun
adj_noun_concrete <- adj_noun_utts %>%
  mutate(adj_stem = wordStem(adj),
         noun_stem = wordStem(noun)) %>%
  filter(adj %in% most_concrete$Word &
         noun_stem %in% most_concrete$stem) %>%
  distinct()


adj_noun_concrete %>% 
  count(adj) %>%
  arrange(desc(n))

adj_noun_concrete %>% 
  count(noun)  %>%
  arrange(desc(n)) 

adj_noun_concrete %>% 
  count(adj, noun) %>%
  arrange(desc(n))


```

#check thresholds
```{r}
looser_concrete <- concrete_concepts %>%
  mutate(conc_rank = ntile(Conc.M,10)) %>%
  arrange(desc(Conc.M)) %>%
  filter(conc_rank >= 7)

#filter different levels for adj and noun
adj_noun_concrete_half <- adj_noun_utts %>%
  mutate(adj_stem = wordStem(adj),
         noun_stem = wordStem(noun)) %>%
  filter(adj %in% looser_concrete$Word &
         noun_stem %in% most_concrete$stem) %>%
  distinct()

loose_adj <- adj_noun_concrete_half %>% 
  count(adj) %>%
  arrange(desc(n)) %>% pull(adj)

orig_adj <- adj_noun_concrete %>% 
  count(adj) %>%
  arrange(desc(n)) %>% pull(adj)

loose_adj[! loose_adj %in% orig_adj]


orig_pairs <- adj_noun_concrete %>% 
  count(adj, noun) %>%
  arrange(desc(n))

loose_pairs <- adj_noun_concrete_half %>% 
  count(adj, noun) %>%
  arrange(desc(n))

loose_pairs %>%
  anti_join(orig_pairs)

```


```{r}
#read in the judgment data
old_turk_counts <- read.csv("data/judgments_session.csv")
final_adjs <- old_turk_counts %>% distinct(adj) %>% pull(adj)
final_nouns <- old_turk_counts %>% distinct(noun) %>% pull(noun)
```
  
#get utt level
```{r}
tmp <- adj_noun_utts %>% 
  mutate(noun_stem = wordStem(noun)) %>%
  mutate(adj_stem = wordStem(adj)) %>%
  filter(noun_stem %in% wordStem(final_nouns)) %>%
  filter(adj_stem %in% wordStem(final_adjs))

judgements <- full_turk_counts %>% distinct(adj, noun, adj_stem, noun_stem, x1, x2, x3, x4, x5, mean_typ)

final_utts <- 
  tmp %>% 
  filter(subject %in% typ_kids) %>%
  left_join(judgements) %>% 
  filter(!is.na(mean_typ))

final_utts %>% count(adj, noun)

final_utts %>% count(adj, noun) %>% arrange(desc(n))
```


#session usage plot by typicality judgments
```{r}
#take session level usage
#  plot overall frequencies at each session
full_turk_counts_plot <- full_turk_counts
full_turk_counts_plot$session2 <- cut(full_turk_counts_plot$session, 
                   breaks=c(0, 2, 4, 6, 8, 10, 12),
                   labels = c(14, 22, 30, 38, 42, 50))
                   # breaks=c(0, 3, 6, 9, 12, 10, 12))

full_expanded <- full_turk_counts[rep(row.names(full_turk_counts), full_turk_counts$n), 1:17]

final_utts %>%
  mutate(typicality=mean_typ) %>%
  mutate(age = (4*session + 10)) %>%
  # filter(age <= 38) %>%
  group_by(session) %>%
  mutate(age=min(age)) %>% 
  ggplot( aes(x=as.numeric(typicality), y=age, group=age, fill=age)) +
  geom_density_ridges2() +
  ylab("Child Age (months)") +
  xlab("More Atypical                                                    More Typical \n   Typicality of adjective-noun pairs") +
  ggtitle("Density plot of parents' adjective use across development") +
  # geom_mark_rect(aes(filter= typicality >= 6, y=15.5)) +
  # geom_mark_rect(aes(filter= typicality >= 6, y=60)) +
  theme_minimal() +
  scale_fill_gradient(low="cornsilk", high=muted("red")) +
  theme(panel.grid = element_line(color="lightgrey",size=0.5),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(),
    axis.text = element_text(size=20),
    axis.text.x = element_text(angle=30, hjust=1)) +
  # scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1))+
  scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1), labels = c('never', 'rarely', 'sometimes', 'about half', 'often', 'almost always', 'always')) +
  scale_y_continuous(minor_breaks = seq(14, 42, 4), breaks = seq(14, 38, 4))
  

```


#session prototypicals plot by typicality judgments
```{r}
#look for prototypicals
#  defined as anything 5 or higher, "somewhat typical" to "extremely  typical"
prototypicals <- final_utts %>% 
  mutate(typicality=mean_typ) %>%
  group_by(session, typicality) %>%
  summarize(sum=n()) %>%
  mutate(howTyp = if_else(typicality>=5, T, F)) %>%
  group_by(session, howTyp) %>%
  summarize(sum=sum(sum)) %>%
  mutate(prop=sum/sum(sum)) %>%
  filter(howTyp)


prototypicals %>%
  mutate(age = (4*session + 10)) %>%
  ggplot(aes(x=age,y=prop, colour=age)) +
  geom_smooth(method= loess, color= "black")+
  geom_point(aes(fill=age), colour="black",pch=21, size=5) +
  ylab("Proportion of modifiers that rated as \n typical of modified noun") +
  xlab("Child's Age (months)") +
  scale_x_continuous(minor_breaks = seq(14, 58, 4), breaks = seq(14, 58, 4))+
  theme_minimal() +
  scale_fill_gradient(low="cornsilk", high=muted("red")) +
  theme(axis.line = element_line(colour = "black"),
        axis.ticks = element_line(),
        axis.text = element_text(size=20),
        panel.grid = element_line(color="lightgrey",size=0.5))
```


#aoas
```{r}
aoas <- read_csv('data/aoas.csv')

full_aoas <- full_expanded %>%
  left_join(aoas, by=c("noun" = "word")) %>%
  mutate(typicality = mean_typ) %>%
  mutate(age = (4 * session + 10)) %>%
  mutate(acquired = if_else(predicted <= age, T, F)) %>%
  filter(! is.na(acquired)) %>%
  as_tibble()
```


```{r predicting-typicality}
freqs <- read_csv(here("data/full_freq.csv"))

tidy_aoas <- freqs %>%
  select(predicted, age, adj, noun, x1:x5, word_freq, mod_freq, prop_mod) %>%
  pivot_longer(cols = x1:x5, names_to = "rater", values_to = "score") %>%
  filter(!is.na(score))

lmer(score ~ log(age) + log(predicted) + scale(log(word_freq)) +
       (1|noun) + (1|adj), tidy_aoas) %>%
  summary()

glmer(cbind(mod_freq, word_freq - mod_freq) ~ log(predicted) + score +
       (1|noun) + (1|adj), family = "binomial", tidy_aoas) %>%
  summary()
```


```{r}
#problem- small range? can't really do the 'acquired' thing
range(full_aoas$predicted)


full_aoas$aoa_bin <- cut(full_aoas$predicted, 
                   # breaks=c(18, 20, 22, 24, 26, 28, 30, 34))
                   breaks=c(18, 22, 26, 30, 34))

full_aoas %>%
  ggplot(aes(x=(predicted), y= (typicality))) +
  geom_jitter() +
  geom_smooth()


full_aoas %>%
  mutate(early = if_else(predicted < median(full_aoas$predicted), T, F)) %>%
  filter(age <= 34) %>%
  ggplot(aes(x=as.numeric(typicality), y=age, group=age, fill=age)) +
  geom_density_ridges2() +
  facet_grid(.~early)

```




#overall word freq
```{r}
# need to know overall word frequency to normalize or do conditional probability
word_freq  <- total_utts %>%
  count(stem, sort=TRUE) %>%
  rename(word_freq = n)

modified_freq <- adj_noun_utts %>%
  count(noun, sort=TRUE) %>%
  rename(mod_freq = n)

full_freq <- full_aoas %>%
  left_join(word_freq, by=c("noun_stem" = "stem")) %>%
  left_join(modified_freq, by=c("noun" = "noun")) %>%
  mutate(prop_mod = mod_freq/word_freq)

full_freq %>% 
  group_by(predicted, age) %>%
  summarize(mean = mean(prop_mod)) %>%
  ggplot(aes(x=predicted, y=mean, group=age))+geom_point() + facet_wrap(~age)+
  geom_smooth()

full_freq %>% 
  group_by(word_freq) %>%
  summarize(mean = mean(prop_mod)) %>%
  ggplot(aes(x=log(word_freq), y=mean))+geom_point() + 
  # facet_wrap(~age)+
  geom_smooth(method=lm)

```







tag the true prenominals?
```{r}
adj_noun_concrete_utts <- adj_noun_utts %>%
  mutate(adj_stem = wordStem(adj),
         noun_stem = wordStem(noun)) %>%
  filter(adj %in% most_concrete$Word &
         noun_stem %in% most_concrete$stem) %>%
  distinct()

tmp <- tagged %>%
  inner_join(adj_noun_concrete_utts %>% select(subject, p_chat, utt_id, noun, adj), by=c("subject", "p_chat", "utt_id"))


judgements <- full_turk_counts %>% distinct(adj, noun, adj_stem, noun_stem, x1, x2, x3, x4, x5, mean_typ, article)

prenominals <- tmp %>%
  group_by(p_chat, utt_id) %>%
  mutate(lag_word = lag(word)) %>%
  filter(noun == word) %>%
  mutate(prenominal = if_else(lag_word == adj, T, F)) %>%
  filter(noun %in% final_nouns & adj %in% final_adjs) %>% 
  left_join(judgements) %>% 
  filter(! is.na(mean_typ)) %>%
  mutate(prenominal = if_else(is.na(prenominal), F, prenominal)) 

final_utts[! final_utts$utt_id %in% prenominals$utt_id , ]
final_utts %>% count(utt_id) %>% arrange(desc(n))
prenominals %>% count(utt_id) %>% arrange(desc(n))


prenominals %>%
  ungroup() %>%
  count(prenominal) %>%
  mutate(prop = n/sum(n))

token_data <- prenominals %>% 
  left_join(concrete_concepts, by = c("noun"="Word")) %>% select(-stem.y) %>% 
  left_join(word_freq, by = c("noun_stem"="stem")) %>% 
  rename(noun_freq = word_freq,
         noun_conc = Conc.M) %>%
  #remove actual utterances for LDP privacy
  ungroup() %>%
  select(-p_chat, -p_mor, -PoS, -word, -stem.x, -lag_word, -Conc.SD) %>%
  mutate(age = (4*session + 10))
  


# boot_prenominals <- prenominals %>%
#   mutate(typicality = mean_typ) %>%
#   filter(!is.na(prenominal)) %>%
#   mutate(age = (4*session.x + 10)) %>%
#   group_by(age, prenominal) %>%
#   tidyboot_mean(typicality)
# 
# boot_prenominals %>%  
#   ggplot(aes(x=prenominal, y=mean, fill= prenominal)) +
#   geom_bar(stat='identity') +
#   geom_linerange(aes(ymin=ci_lower, ymax=ci_upper)) +
#   facet_wrap(~age) +
#   coord_cartesian(ylim=c(2.6,3.6))
```


```{r}


prenominals %>% 
  mutate(age = (4*session + 10)) %>%
  # filter(age <= 38) %>%
  group_by(session, prenominal) %>%
  mutate(age=min(age)) %>%
  ggplot( aes(x=as.numeric(mean_typ), y=age, group=age, fill=age)) +
  geom_density_ridges2() +
  ylab("Child Age (months)") +
  xlab("More Atypical                                                    More Typical \n   Typicality of adjective-noun pairs") +
  ggtitle("Density plot of parents' adjective use across development") +
  # geom_mark_rect(aes(filter= typicality >= 6, y=15.5)) +
  # geom_mark_rect(aes(filter= typicality >= 6, y=60)) +
  theme_minimal() +
  scale_fill_gradient(low="cornsilk", high=("red")) +
  theme(panel.grid = element_line(color="lightgrey",size=0.5),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(),
    axis.text = element_text(size=20),
    axis.text.x = element_text(angle=30, hjust=1)) +
  # scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1))+
  scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1), labels = c('never', 'rarely', 'sometimes', 'about half', 'often', 'almost always', 'always')) +
  # scale_y_continuous(minor_breaks = seq(14, 42, 4), breaks = seq(14, 38, 4))+
  facet_wrap(~ prenominal)
```


```{r}
tmp <- prenominals %>% filter(prenominal) %>% ungroup() %>%
  select(subject, session, noun, adj, prenominal, x1, x2, x3, x4, x5, mean_typ)


prototypicals <- prenominals %>% 
  mutate(typicality=mean_typ) %>%
  mutate(howTyp = if_else(typicality>=5, T, F)) %>%
  group_by(session, prenominal, howTyp) %>%
  summarize(sum=n()) %>%
  mutate(prop=sum/sum(sum)) %>%
  filter(howTyp, prenominal)


prototypicals %>%
  mutate(age = (4*session + 10)) %>%
  ggplot(aes(x=age,y=prop, colour=age, linetype = prenominal)) +
  geom_smooth(method= loess, color= "black")+
  geom_point(aes(fill=age), colour="black",pch=21, size=5) +
  ylab("Proportion of modifiers that rated as \n typical of modified noun") +
  xlab("Child's Age (months)") +
  scale_x_continuous(minor_breaks = seq(14, 58, 4), breaks = seq(14, 58, 4))+
  theme_minimal() +
  scale_fill_gradient(low="cornsilk", high=muted("red")) +
  theme(axis.line = element_line(colour = "black"),
        axis.ticks = element_line(),
        axis.text = element_text(size=20),
        panel.grid = element_line(color="lightgrey",size=0.5))
```




#Adult speech
```{r}
coca <- read_feather("data/coca_counts.feather")

tmp <- coca %>%
  mutate(adj_stem = wordStem(adj),
         noun_stem = wordStem(noun)) %>%
  mutate(adult_freq = n) %>%
  filter(adj %in% most_concrete$Word &
         noun_stem %in% most_concrete$stem) 

missed <- full_turk_counts %>%
  distinct(adj, noun, adj_stem, noun_stem, mean_typ) %>%
  # left_join(tmp %>% group_by(adj, noun) %>% summarize(adult_freq=sum(adult_freq)), by=c("adj", "noun")) %>%
  left_join(tmp, by=c("adj_stem", "noun_stem")) %>%
  filter(is.na(adult_freq))

cocaonlypairs <- tmp %>%
  distinct(adj,noun,adult_freq) %>%
  left_join(judgements, by=c("adj", "noun")) %>%
  filter(is.na(mean_typ)) %>%
  select(adj,noun,adult_freq) %>%
  filter(adult_freq > 30)
  
ggplot(cocaonlypairs %>% filter(adult_freq < 200, adult_freq > 20), aes(adult_freq)) +
  geom_histogram()

adult_types <- full_turk_counts %>%
  distinct(adj, noun, adj_stem, noun_stem, mean_typ) %>%
  # left_join(tmp %>% group_by(adj, noun) %>% summarize(adult_freq=sum(adult_freq)), by=c("adj", "noun")) %>%
  left_join(tmp, by=c("adj_stem", "noun_stem")) %>%
  filter(!is.na(adult_freq))
  
adult <- adult_types[rep(row.names(adult_types), adult_types$adult_freq), 1:8] 

adult %>%
  ggplot(aes(x=as.numeric(mean_typ), y=type, group=type, fill=type)) +
  geom_density_ridges2() +
  ylab("Source of Adult Speech (e.g., written)") +
  xlab("More Atypical                                                    More Typical \n   Typicality of adjective-noun pairs") +
  ggtitle("Density plot of parents' adjective use across development") +
  theme_minimal() +
  theme(panel.grid = element_line(color="lightgrey",size=0.5),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(),
    axis.text = element_text(size=20),
    axis.text.x = element_text(angle=30, hjust=1)) +
  geom_vline(xintercept = 4) +
    scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1), labels = c('never', 'rarely', 'sometimes', 'about half', 'often', 'almost always', 'always'))

adult %>%
  mutate(who="") %>%
  ggplot(aes(x=as.numeric(mean_typ), y=who)) +
  geom_density_ridges2(binwidth = .133) +
  ylab("Source of Adult Speech (e.g., written)") +
  xlab("More Atypical                                                    More Typical \n   Typicality of adjective-noun pairs") +
  ggtitle("Density plot of parents' adjective use across development") +
  theme_minimal() +
  theme(panel.grid = element_line(color="lightgrey",size=0.5),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(),
    axis.text = element_text(size=20),
    axis.text.x = element_text(angle=30, hjust=1)) +
  geom_vline(xintercept = 4) +
    scale_x_continuous(minor_breaks = seq(1 , 7, 1), breaks = seq(1, 7, 1), labels = c('never', 'rarely', 'sometimes', 'about half', 'often', 'almost always', 'always'))
```

```{r}

#look for prototypicals
#  defined as anything 5 or higher, "somewhat typical" to "extremely  typical"
prototypicals <- adult %>% 
  mutate(typicality=mean_typ) %>%
  mutate(howTyp = if_else(typicality>=5, T, F)) %>%
  group_by(type, howTyp) %>%
  summarize(sum=n()) %>%
  mutate(prop=sum/sum(sum)) %>%
  filter(howTyp)


prototypicals %>%
  ggplot(aes(x=type,y=prop, colour=age)) +
  # geom_smooth(method= loess, color= "black")+
  geom_point(aes(fill=type), colour="black",pch=21, size=5) +
  ylab("Proportion of modifiers that rated as \n typical of modified noun") +
  theme_minimal() +
  theme(axis.line = element_line(colour = "black"),
        axis.ticks = element_line(),
        axis.text = element_text(size=20),
        panel.grid = element_line(color="lightgrey",size=0.5))
```






