---
title: "Pilot Data and Preliminary Checks on Purple vs. Orange Carrots"
author: "ben morris"
date: "3/14/2019"
output: html_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(childesr)
library(tictoc)
library(wordbankr)
library(SnowballC)

knitr::opts_chunk$set(fig.align='center', echo=FALSE, messages=FALSE, warning = FALSE,
                      fig.height = 3, fig.width=5)

```


#***
# Read in the carrots
#***

If you need to pull more data from childes, use the pilot_fetch_data.Rmd code. 

```{r, include = FALSE}
#just read in the data
color_adjectives <- c("red", "orange", "yellow", "green", "blue", "purple", "white", "brown", "pink", "black")

full <- read_csv("3.6.2019_pilot.csv") 
```


```{r}
#how much description (of ANY kind)
   #i.e. amount of adjective use
full %>%
  group_by(grepl("adj", part_of_speech)) %>%
  summarize(n=n()) %>%
  mutate(pro=n/sum(n))


#how much color description 
full %>%
  group_by(isColorDescribed) %>%
  summarize(n=n()) %>%
  mutate(pro=n/sum(n))

#breakdown of typicality 
    #--> most modificaitons are 'atypical'
        #that's inflated by coding any other color word as atypical
full %>%
  group_by(isColorDescribed, adj_freq) %>%
  summarize(n=n()) %>%
  ungroup() %>%
  mutate(pro=n/sum(n))
```

- Adjectives are used in `r nrow(full %>% filter(grepl("adj", part_of_speech)))/nrow(full)*100`% of utterances that include one of our target nouns (also looking at window size 2). 

- We are specifically going after the following adjectives used to describe these nouns: `r color_adjectives` (also looking at window size 2).

- Our target color words are used in `r (nrow(full %>% filter(adj!="none"))/nrow(full)*100)`% of utterances that include one of our target words (also looking at window size 2). 


#Overall Color Adjective Use x Typicality
```{r}
prop_use_overall <- full %>%
  group_by(adj_freq) %>%
  summarize(n=n()) %>%
  mutate(adj_freq = factor(adj_freq, 
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  mutate(prop=n/sum(n)) %>%
  filter(adj_freq != "none")


ggplot(prop_use_overall, aes(x = adj_freq, y = prop, color=adj_freq)) +
  geom_point(size=2) +
  coord_cartesian(ylim=c(0,0.02))+
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion of Total Utterances Including Target Word")
```

#By item
```{r}
prop_use_item <- full %>%
  group_by(stem, adj_freq, prototypicals) %>%
  summarize(n=n()) %>%
  group_by(stem) %>%
  mutate(prop=n/sum(n)) %>%
  select(-n) %>%
  mutate(adj_freq = factor(adj_freq,
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  complete(stem, adj_freq, fill = list("prop" = 0)) %>%
  filter(prototypicals!=TRUE) %>%
  filter(adj_freq != "none")

ggplot(prop_use_item, aes(x = adj_freq, y = prop, color=adj_freq)) +
  facet_wrap(~ stem, nrow=4, ncol=5) +
  geom_point(size=2) +
  # coord_cartesian(ylim=c(0,0.02))+
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion of Total Utterances Including Target Word")
```


#By adjective position relative to noun (very coarsely!)
```{r}
prop_use_position <- full %>%
  group_by(adj_freq, placement) %>%
  summarize(n=n()) %>%
  ungroup() %>%
  mutate(adj_freq = factor(adj_freq,
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  group_by(adj_freq) %>%
  mutate(prop=n/sum(n)) %>%
  filter(adj_freq != "none")

ggplot(prop_use_position, aes(x = adj_freq, y = prop, color=placement)) +
  geom_point(size=2) +
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion Of Those Modifications")
```



