---
title: "Pilot Data and Preliminary Checks on Purple vs. Orange Carrots"
author: "ben morris"
date: "3/14/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(childesr)
library(tictoc)
library(wordbankr)
library(SnowballC)

knitr::opts_chunk$set(fig.align='center', echo=FALSE, messages=FALSE, warning = FALSE,
                      fig.height = 3, fig.width=5)

```


#find carrots
```{r, include = FALSE}
## get the early acquired nouns
# eng_ws_data <- get_instrument_data(language = "English (American)",
#                                    form = "WS",
#                                    administrations = TRUE,
#                                    iteminfo = TRUE)
# 
# wordbank_aoas <- fit_aoa(eng_ws_data, measure = "understands", method = "glmrob") %>%
#   arrange(aoa)
# 
# wordbank_nouns <- wordbank_aoas %>% filter(lexical_category=="nouns")
# wordbank_nouns <- wordbank_nouns[1:200,]
# wordbank_nouns_200 <- wordbank_nouns$definition

#scan for good color words for pilot
targets <- c("banana", "apple", "bear", "pig", "grapes", "grass", "tiger",
                "carrots", "corn", "sky", "pumpkin", "egg", "cloud", "bear")

```


Going after the following words as an initial pilot test to dig into the structure in these utterances. These words include `r targets`. We take a window of 2 utterances (i.e. 2 utterances before target, and 2 utterances folowing the target).

#Scrape the data from CHILDES
```{r}
#improved function for fetching target CHILDES utterances with a set window
get_contexts <- function(corpus, token, window) {
  
  seq <- window[1]:window[2]
  
  utts <- dplyr::tbl(con, "utterance")
  
  my_corpus_id <- dplyr::tbl(con, "corpus") %>%
    filter(name == corpus) %>%
    pull(id)
  
  ids <- dplyr::tbl(con, "token") %>%
    filter(corpus_id == my_corpus_id, gloss == token) %>%
    select(utterance_id) %>%
    pull()
  
  context_pos <- function(pos) {

    #added if statement to deal with cases where no instance of that token is found in a given transcript
    if(length(ids)>0) {
      sub_utts <- utts %>% 
        filter(id %in% ids) %>%
        select(transcript_id, utterance_order) %>%
        mutate(utterance_order = utterance_order + pos) 
      
      utts %>% 
        inner_join(sub_utts, by = c("utterance_order", "transcript_id")) %>%
        collect() %>%
        mutate(pos = pos,
               target= wordStem(token))
    }
  }
  
  map_df(seq, context_pos) %>%
    arrange(transcript_id, pos)
}
```

```{r}
targetsToSearch <- c('carrot', 'carrots', 'apple','apples', 'banana', 'banana', 'grape', 'grapes',
                     'tiger', 'tigers', 'pumpkin', 'pumpkins', 'corn', 'sky','grass', 'egg', 'eggs',
                     'tomato', 'tomatoes', 'cloud','cloouds', 'bear','bears')
# corpora <- c('Providence', 'Thomas')
corpora_eng <- get_corpora() %>%
  filter(collection_name=="Eng-NA") %>%
  pull(corpus_name)

corpora <- corpora_eng[1:length(corpora_eng)]

#read in all data for North American English corpora
con <- connect_to_childes()
full <- data.frame(NULL)
for (i in 1:length(corpora)) {
  this_corpus <- corpora[i]
  try(
    for (j in 1:length(targetsToSearch)) {
      this_word = targetsToSearch[j]
      full <- 
        bind_rows(full, 
                  get_contexts(corpus=this_corpus, this_word, window=c(-2,2)))
    }
  )
}
```

```{r}
full <- full %>%
  mutate(adj="none",
         adj_freq = "none",
         placement = "none") %>%
  mutate(stem = wordStem(target))
```

```{r}
#read in typicality df
typicality <- read.csv("typicality_BM.csv") %>% select(-X)


#grab every adjective, and see if it is a typical color for that target, if not, call it atypical
modified_full <- data.frame(NULL)
for (i in 1:nrow(typicality)) {
  word= typicality$stemTargets[i] 
    print(word)
  # word_plural= paste(word, 's', sep='')
  prototype = typicality$prototypical[i]
  semitype = typicality$semitypical[i]
  lesstype = typicality$lesstypical[i]
  lesstype2 = typicality$lesstypical2[i]

      
  this_word <- full %>%
    filter(stem==word) %>%
        rowwise() %>%
        mutate(adj_freq = if_else(adj != "none", "atypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == prototype, "prototypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == semitype, "semitypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == lesstype, "semitypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == lesstype2, "semitypical", adj_freq)) %>%
        mutate(placement = if_else(adj=="none", "none",
          if_else(gregexpr(adj, gloss)[[1]][1] < gregexpr(target, gloss)[[1]][1], "pre", "post")
          ))

  modified_full <- bind_rows(modified_full, this_word)
}
```

```{r}
# get color adjectives
full <- full %>%  
  mutate(adj= if_else(grepl("orange", gloss), "orange", adj)) %>%
  mutate(adj= if_else(grepl("purple", gloss), "purple", adj)) %>%
  mutate(adj= if_else(grepl("white", gloss), "white", adj)) %>%
  mutate(adj= if_else(grepl("brown", gloss), "brown", adj)) %>%
  mutate(adj= if_else(grepl("yellow", gloss), "yellow", adj)) %>%
  mutate(adj= if_else(grepl("red", gloss), "red", adj)) %>%
  mutate(adj= if_else(grepl("green", gloss), "green", adj)) %>%
  mutate(adj= if_else(grepl("pink", gloss), "pink", adj)) %>%
  mutate(adj= if_else(grepl("blue", gloss), "blue", adj)) %>%
  mutate(adj= if_else(grepl("black", gloss), "black", adj))


color_adjectives <- c("red", "orange", "yellow", "green", "blue", "purple", "white", "brown", "pink", "black")


```


#Also get these prototypical color ones
```{r}
targetsToSearch <- c("lemon", "lemons", "milk", "frog", "pea", "peas", "yogurt", "yogurts", "chocolate", "chocolates")
prototypicals <- data.frame(NULL)
for (i in 1:length(corpora)) {
  this_corpus <- corpora[i]
  try(
    for (j in 1:length(targetsToSearch)) {
      this_word = targetsToSearch[j]
      prototypicals <- 
        bind_rows(prototypicals, 
                  get_contexts(corpus=this_corpus, token=this_word, window=c(-2,2)))
    }
  )
}


modified_prototypicals <- data.frame(NULL)

targets <- c('lemon', 'milk', 'frog','chocolate','pea','yogurt')
prototypical <- c('yellow', 'white', "green", "brown", "green", "white")
stemTargets <-  wordStem(targets)
prototypicality <- data.frame(stemTargets, prototypical)


# get color adjectives
prototypicals <- prototypicals %>%  
  mutate(adj= if_else(grepl("orange", gloss), "orange", adj)) %>%
  mutate(adj= if_else(grepl("purple", gloss), "purple", adj)) %>%
  mutate(adj= if_else(grepl("white", gloss), "white", adj)) %>%
  mutate(adj= if_else(grepl("brown", gloss), "brown", adj)) %>%
  mutate(adj= if_else(grepl("yellow", gloss), "yellow", adj)) %>%
  mutate(adj= if_else(grepl("red", gloss), "red", adj)) %>%
  mutate(adj= if_else(grepl("green", gloss), "green", adj)) %>%
  mutate(adj= if_else(grepl("pink", gloss), "pink", adj)) %>%
  mutate(adj= if_else(grepl("blue", gloss), "blue", adj)) %>%
  mutate(adj= if_else(grepl("black", gloss), "black", adj))

for (i in 1:nrow(prototypicality)) {
  word= prototypicality$stemTargets[i] 
  prototype = prototypicality$prototypical[i]

  this_word <- prototypicals %>%
    filter(stem==word) %>%
        rowwise() %>%
        mutate(adj_freq = if_else(adj != "none", "atypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == prototype, "prototypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == semitype, "semitypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == lesstype, "semitypical", adj_freq)) %>%
        mutate(adj_freq = if_else(adj == lesstype2, "semitypical", adj_freq)) %>%
        mutate(placement = if_else(adj=="none", "none",
          if_else(gregexpr(adj, gloss)[[1]][1] < gregexpr(target, gloss)[[1]][1], "pre", "post")
        ))

  modified_prototypicals <- bind_rows(modified_prototypicals, this_word)
}
```






```{r}
#join together
full <- bind_rows(modified_prototypicals, modified_full)
#and prune
#  because of windowing, if target utterances are back to back, we will have many utterances that are duplicated in the data set, filter to only distinct utts
full_pilot_pruned <-  full %>% select(-X, -pos) %>% distinct(.)

```

#***
#or just read in the carrots
#***

```{r, include = FALSE}

#just read in the data
full <- read_csv("3.6.2019_pilot.csv") 
```


```{r}
#how much description (of ANY kind)
   #i.e. amount of adjective use
full %>%
  group_by(grepl("adj", part_of_speech)) %>%
  summarize(n=n()) %>%
  mutate(pro=n/sum(n))


#how much color description 
full %>%
  group_by(isColorDescribed) %>%
  summarize(n=n()) %>%
  mutate(pro=n/sum(n))

#breakdown of typicality 
    #--> most modificaitons are 'atypical'
        #that's inflated by coding any other color word as atypical
full %>%
  group_by(isColorDescribed, adj_freq) %>%
  summarize(n=n()) %>%
  ungroup() %>%
  mutate(pro=n/sum(n))
```

- Adjectives are used in `r nrow(full %>% filter(grepl("adj", part_of_speech)))/nrow(full)*100`% of utterances that include one of our target nouns (also looking at window size 2). 

- We are specifically going after the following adjectives used to describe these nouns: `r color_adjectives` (also looking at window size 2).

- Our target color words are used in `r (nrow(full %>% filter(adj!="none"))/nrow(full)*100)`% of utterances that include one of our target words (also looking at window size 2). 


#Overall Color Adjective Use x Typicality
```{r}
prop_use_overall <- full %>%
  group_by(adj_freq) %>%
  summarize(n=n()) %>%
  mutate(adj_freq = factor(adj_freq, 
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  mutate(prop=n/sum(n)) %>%
  filter(adj_freq != "none")


ggplot(prop_use_overall, aes(x = adj_freq, y = prop, color=adj_freq)) +
  geom_point(size=2) +
  coord_cartesian(ylim=c(0,0.02))+
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion of Total Utterances Including Target Word")
```

#By item
```{r}
prop_use_item <- full %>%
  group_by(stem, adj_freq, prototypicals) %>%
  summarize(n=n()) %>%
  group_by(stem) %>%
  mutate(prop=n/sum(n)) %>%
  select(-n) %>%
  mutate(adj_freq = factor(adj_freq,
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  complete(stem, adj_freq, fill = list("prop" = 0)) %>%
  filter(prototypicals!=TRUE) %>%
  filter(adj_freq != "none")

ggplot(prop_use_item, aes(x = adj_freq, y = prop, color=adj_freq)) +
  facet_wrap(~ stem, nrow=4, ncol=5) +
  geom_point(size=2) +
  # coord_cartesian(ylim=c(0,0.02))+
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion of Total Utterances Including Target Word")
```


#By adjective position relative to noun (very coarsely!)
```{r}
prop_use_position <- full %>%
  group_by(adj_freq, placement) %>%
  summarize(n=n()) %>%
  ungroup() %>%
  mutate(adj_freq = factor(adj_freq,
                           levels = c("none", "prototypical", "semitypical", "atypical"))) %>%
  group_by(adj_freq) %>%
  mutate(prop=n/sum(n)) %>%
  filter(adj_freq != "none")

ggplot(prop_use_position, aes(x = adj_freq, y = prop, color=placement)) +
  geom_point(size=2) +
  theme(axis.text.x=element_text(angle=25,hjust=.9))+
  xlab("Adjective Typicality") + ylab("Proportion Of Those Modifications")
```



